Compilation through interpretation

### 2023-07-18 Papers/FEDCIS-2023/cm1.tex
stuff -_-

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{graphicx}
\usepackage{listings}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline}
\bibliographystyle{acm}

@@

\author{
	\IEEEauthorblockN{Adam Grabski}
	\IEEEauthorblockA{0000-0002-6283-8461\\
		Warsaw Univeristy of Technology\\
		in Warsaw\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: adam.gr@outlook.com}
	\and
	\IEEEauthorblockN{Ilona Bluemke}
	\IEEEauthorblockA{0000-0002-2894-5976\\
		Warsaw Univeristy of Technology\\
		in Warsaw\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: Ilona.Bluemke@pw.edu.pl}
}

>>>>

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{graphicx}
\usepackage{listings}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline}
\bibliographystyle{IEEEtran}

@@

\author{
	\IEEEauthorblockN{Adam Grabski}
	\IEEEauthorblockA{0000-0002-6283-8461\\
		Warsaw Univeristy of Technology\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: adam.gr@outlook.com}
	\and
	\IEEEauthorblockN{Ilona Bluemke}
	\IEEEauthorblockA{0000-0002-2894-5976\\
		Warsaw Univeristy of Technology\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: Ilona.Bluemke@pw.edu.pl}
}

### 2023-07-18 Papers/FEDCIS-2023/sections/design.tex
stuff -_-

	\begin{lstlisting}[
	  numbers=left,
	  firstnumber=0,
	  caption={noDiscard attribute in C-=-1},
	  aboveskip=0pt,
	  label={lst:noDiscardCm1}
	  ]
public att<function> NoDiscard
{
	public fn attach(f: functionDescriptor)
	{}
	public fn onCall(call: functionCallExpression*)
	{
		if(call._parentStatment != null<IInstruction>())
			raiseError(
			&(call._pointerToSource),
			"Return value of a no-discard function is not used",
			123
			);
}
}
  \end{lstlisting}
\end{minipage}

>>>>

	\begin{lstlisting}[
	  numbers=right,
	  firstnumber=0,
	  caption={noDiscard attribute in C-=-1},
	  aboveskip=0pt,
	  label={lst:noDiscardCm1}
	  ]
public att<function> NoDiscard
{
	public fn attach(f: functionDescriptor)
	{}
	public fn onCall(call: functionCallExpression*)
	{
		if(call._parentStatment != null<IInstruction>())
			raiseError(
			&(call._pointerToSource),
			"Return value of a no-discard function is not used",
			123
			);
}
}
  \end{lstlisting}
\end{minipage}

### 2023-07-18 Papers/FEDCIS-2023/sections/implementation.tex
stuff -_-

	\begin{lstlisting}[
	  numbers=left,
	  firstnumber=0,
	  caption={Part of a Backend Interface, using \lstinline{ISymbolNameOverride} interface},
	  aboveskip=0pt,
	  label={lst:selected_Backend_interface}
	  ]
  private fn getFunctionName(f: functionDescriptor) -> string {
	let attribute = f.get_attribute<ISymbolNameOverride>();
	if(attribute != null<ISymbolNameOverride>())
	  return attribute.createSymbolName();
	return mangleName(f);
  }
  private fn buildFunction(
	f: functionDescriptor,
	llvmF: llvmFunction,
	registry: packageRegistry*,
	mod: llvmModule)
  {
	let variables = dictionary<variableDescriptor, llvmValue>();
	let params = f.parameters();
	for(i in enumerate(0, params.length()))
	  variables.push(params[i], llvmF.getParameter(i));
	let builder = llvmF.getBuilder();
	let attribute = f.get_attribute<ISymbolNameOverride>();
	if(attribute == null<ISymbolNameOverride>())
	{
	  let code = f.code();
	  build_block(&code, &builder, &variables, registry);
	}
  }
  \end{lstlisting}
\end{minipage}

>>>>

\begin{minipage}{8cm}
	\centering
	\begin{lstlisting}[
	  numbers=right,
	  firstnumber=0,
	  caption={Part of a Backend Interface, using \lstinline{ISymbolNameOverride} interface},
	  aboveskip=0pt,
	  label={lst:selected_Backend_interface}
	  ]
  private fn getFunctionName(f: functionDescriptor) -> string {
	let attribute = f.get_attribute<ISymbolNameOverride>();
	if(attribute != null<ISymbolNameOverride>())
	  return attribute.createSymbolName();
	return mangleName(f);
  }
  private fn buildFunction(
	f: functionDescriptor,
	llvmF: llvmFunction,
	registry: packageRegistry*,
	mod: llvmModule)
  {
	let variables = dictionary<variableDescriptor, llvmValue>();
	let params = f.parameters();
	for(i in enumerate(0, params.length()))
	  variables.push(params[i], llvmF.getParameter(i));
	let builder = llvmF.getBuilder();
	let attribute = f.get_attribute<ISymbolNameOverride>();
	if(attribute == null<ISymbolNameOverride>())
	{
	  let code = f.code();
	  build_block(&code, &builder, &variables, registry);
	}
  }
  \end{lstlisting}
\end{minipage}

### 2023-07-18 Papers/FEDCIS-2023/sections/realted-work.tex
corrections from FEDCIS review process
stuff -_-

C\# compiler, called Roslyn \cite{roslyn}, has the closest set of capabilities to what CTFEF aims to achieve.
Its architecture allows for user-defined analyzers and code generators using a program model generated by the compiler \cite{vermeir2022net}.
These compiler extensions can be used and distributed as regular code packages, for example using nuget package manager \cite{balliauw2013nuget}.
C\# code analyzers have access to entire analyzed code-base and to semantic analysis functionality of the compiler.
Using CTFEF for the purposes of code analysis would not offer any additional benefits.

@@

Although CTFEF was inspired by the C\# compiler, there are significant differences between them.
C\# compiler extensions are separate, compiled, dynamic libraries loaded by the compiler and executed as a regular code.
In CTFEF components that analyze and generate code are part of regular code base and are not compiled separately.
The intermediate representation of these modules is interpreted at compile time, together with other parts of compiler, and operate on the same representation of user program.
CTFEF is further described in chapter \ref{compiler-design}.

>>>>

C\# compiler, called Roslyn \cite{vermeir2022net}, has the closest set of capabilities to what CTFEF aims to achieve.
Its architecture allows for user-defined analyzers and code generators using a program model generated by the compiler \cite{vermeir2022net}.
These compiler extensions can be used and distributed as regular code packages, for example using nuget package manager \cite{balliauw2013nuget}.
C\# code analyzers have access to entire analyzed code-base and to semantic analysis functionality of the compiler.
Using CTFEF for the purposes of code analysis would not offer any additional benefits.

@@

Although CTFEF was inspired by the C\# compiler, there are significant differences between them.
C\# compiler extensions are separate, compiled, dynamic libraries loaded by the compiler and executed as a regular code.
In CTFEF components that analyze and generate code are part of regular code base and are not compiled separately.
The intermediate representation of these modules is interpreted at compile time, together with other parts of compiler, and operate on the same representation of user program.
CTFEF is further described in section \ref{compiler-design}.
